To Do List

### 2019-05-22 Papers.Rmd
Add note that  CTCF is not at TAD boundaries, but nearby
Add Twitter tread on class imbalance

@@

@@

>>>>

- Krietenstein, Nils, Sameer Abraham, Sergey Venev, Nezar Abdennur, Johan Gibcus, Tsung-Han Hsieh, Krishna Mohan Parsi, et al. “Ultrastructural Details of Mammalian Chromosome Architecture.” Preprint. Genomics, May 17, 2019. https://doi.org/10.1101/639922. - Micro-C (MNase digestion Hi-C) technology and basic analysis. human embryonic stem cells H1-ESC and differentiated human foreskin fibroblasts (HFFc6). Captures standard Hi-C features, with many additional interaction peaks ("dots"). Enrichment of classical marks of TAD boundaries (Fig 3C) - RAD21, TAF1, PHF8, CTCF, TBP, POL2RA, YY1, and more.

@@

- Twitter tread on class imbalance, https://twitter.com/goodfellow_ian/status/1127994332416364549

@@

- CTCF is not at TAD boundaries, but nearby. "only 15% CTCF sites are at the TAD boundary while 85% CTCF sites are inside the TAD [@Ong:2014aa]."
